#Problem 1
```{r}
X=rmultinom(100000,size=10,prob=c(0.2,0.5,0.3))
mean(X[1,]==2&X[2,]==4&X[3,]==4)
dmultinom(x=c(2,4,4),prob=c(0.2,0.5,0.3))
```
#Problem 2
```{r}
data=replicate(100000,sample(3,size=10,replace=TRUE,prob=c(0.2,0.5,0.3)))
X.1=apply(data,2,function(x) sum(x==1))
X.2=apply(data,2,function(x) sum(x==2))
X.3=apply(data,2,function(x) sum(x==3))
mean(X.1==2&X.2==4&X.3==4)
dmultinom(x=c(2,4,4),prob=c(0.2,0.5,0.3))
```

#Problem 3
```{r}
library(nortest)
data=runif(12*100000,0,1)
data=matrix(data,nrow=12)
Z=apply(data,2,function(x) sum(x)-6)
hist(Z,breaks=50,prob=T)
```

#Problem 4

###(a)
X_~N(7,1)
Y_~N(10,25/12)
W~N(-3,37/12)

###(b)
```{r}
n=100000
X=matrix(rnorm(9*n,7,3),nrow=9)
Y=matrix(rnorm(12*n,10,5),nrow=12)
X_=apply(X,2,mean)
Y_=apply(Y,2,mean)
W=X_-Y_
mean(W)
var(W)
hist(W,breaks=100,prob=T)
```

###(c)
```{r}
pnorm(-1.5,-3,sqrt(37/12))
mean(W< (-1.5))
```

#Problem 5

###(a)
```{r}
n=100000
X=matrix(rexp(30*n,1/3),nrow=30)
X_=apply(X,2,mean)

```

###(b)
Since X_i has the distribution of gamma(1,1/3), the sum of all the X_is has the distribution of gamma(30,1/3). So the sum has the mean of 90, standard deviation of sqrt(270). Thus X_ has the mean of 3, the standard deviation of sqrt(0.3)->0.548
```{r}
mean(X_)
sd(X_)
```

###(c)
```{r}
mean(X_<=3.5)
```

###(d)
It's similar to the value in (c)
```{r}
mu=3
sigma=0.54772
pnorm(3.5,mu,sigma)
```

#Problem 6
We mark the sum of X_i as S(X). We first calculate the expectation and the standard deviation of S(X).

We can first suppose a = 1.

We notice that the characteristic function of any X_i is (e^(it)-1)/(it).

Then we have the characteristic function of S(X) as (e^(it)-1)^n/((it)^n).

Thus the moment generating function of S(X) is M(s)=(e^s-1)^n/(s^n)
We notice that e^s-1=s+(s^2)/2+(s^3)/6+o(s^3), so we have:
M(s)=(1+s/2+(s^2)/6+o(s^2))^n

We notice that (1+x)^n=1+n x + n(n-1)/2 (x^2) + o(x^2), we apply that to M(s), then we have:
M(s)=1 + n(s/2 + (s^2)/6 + o(s^2)) + n(n-1)/2 (s/2+s^2/6+o(s^2))^2 + o(s^2)

By merging the cofficients of first-order and second-order terms and eliminating all the minor terms, we have:
M(s) = 1 + n s / 2 + (3 (n^2) + n) / 24 + o(s^2)

So we got that: E(S(X)) = ns/2 and E(S(X)^2)= (3 (n^2) + n) / 12

That leads to the var of S(X) to be n/12.

When a is not equal to 1, we can simply mark X_i = a Y_i, then we have: 
E(S(Y)) = n/2, var(S(Y))= n/12, E(S(X)) = na/2, var(S(X))=a^2 var(S(Y))= n(a^2)/12

Then we can assert that the expection and variance of sample mean are:
a/2 and (a^2)/(12 n)

Finally we use the CLT approximation, a normal distribution approximation to the sample mean is N(a/2,(a^2)/(12 n))

In the following sample, we choose a=2, n=1000. And from the above formula, we should expect that its mean and std to be 1 and 0.018.

The two results match well.
```{r}
n=1000
m=10000
a=2
X=matrix(runif(n*m,0,a),nrow=n)
X_sum=apply(X,2,sum)
mean(X_sum)
X_=apply(X,2,mean)
mean(X_)
sd(X_)
hist(X_,breaks=100,prob=T)
```