#problem 1
```{r problem1}
  a=(sin(1.23)*(10^11))%%10%/%1
  b=sqrt(a^4+pi*a^3)
  c=floor((log(b)^3)*log(exp(1),10))+1
  d=sum((1:c)^3.5)
  e=floor(d)%%103
  c(a,b,c,d,e)
```

#problem 2
```{r problem2 (a)}
  #the fraction is C(10^8-1,999)/C(10^8,1000)=1000/10^8=1/100000
  1/100000
```

```{r problem2 (b)}
  (1-1e-05)^2000
```

```{r problem2 (c)}
  #if we suppose total adult population is N, sample number is n, and we repeat
  #m times of the test, then we have the fraction in (a) be n / N. So what we        #should solve n for (1-n/N)^m=0.5 given N=10e8 and m=2000
  #The solution is n=10e8 * (1 - 0.5^(1/2000))
  10e8 * (1 - 0.5^(1/2000))
```
#problem 3
```{r problem3}
  data3 <- read.csv("yob2014.txt",header=FALSE)
  names(data3)<-c("name","gender","number")
  prob<-function(data,in_name){
    male=data[(data$name==in_name)&(data$gender=='M'),'number']
    female=data[(data$name==in_name)&(data$gender=='F'),'number']
    return(as.numeric(female)/(male+female))
  }

  newlist=1:10
  for(ii in 1:10){
    newlist[ii]<-prob(data3,data3[ii,1])
  }
  newlist
  order(newlist)
  #Conclusions:The most common name in female babies doesn't have a maximum          #probability value. It illustrates that maybe it's just natural for people to      #come with this kind of names although it's not the most suitable for girls.
```
#problem 4
```{r problem4}
  0.15*0.68+0.26*0.54+0.59*0.29
```

#problem 5
```{r problem5}
  X=runif(100000)
  Y=runif(100000)
  B=as.numeric(Y<sin(pi*X))
  AB=as.numeric(Y<sin(pi*X)&X<=1/3)
  cB=sum(B)
  cAB=sum(AB)
  pB=cB/100000
  pA_B=cAB/cB
  pB_A=cAB/(100000/3)
  cat("p(B)=",pB,"p(A|B)=",pA_B,"p(B|A)=",pB_A)
```

#problem 6
(1)R mainly provides statistical approaches while Python provides more general approaches.
(2)R aims at data-analysis while Python has a more common objective of Deployment and Production.
(3)R users are mainly Scholars and R&D professionals while Python users are mostly Programmers and Developers.
(4)R is used to run locally while Python can be integrated with apps.