```{r}
set.seed(225)
```

#Problem 1

```{r Problem 1-(a)}
mytoss<-function(p){
  return(as.numeric(runif(1)<p))
}
myattempts = function(p){ counter <- 0
while (mytoss(p) == 0){ counter <- counter + 1 }
return(counter) }

  p=0.1;
  result1=replicate(10000,myattempts(p))
  result2=rgeom(10000,p)
  max1=max(result1)
  max2=max(result2)
  m_length=max(max1,max2)
  record1=rep(1,m_length+1)
  record2=rep(1,m_length+1)
  for(i in 0:m_length){
    record1[i+1]=mean(as.numeric(result1==i))
  }
  for(i in 0:m_length){
    record2[i+1]=mean(as.numeric(result2==i))
  }
  record3=dgeom(0:m_length,p)
  df1=data.frame(number=0:m_length,myattempts=record1,rgeom=record2,dgeom=record3)
  df1[1:6,]
```

```{r Problem 1-(b)}
  p=0.3;
  result1=replicate(10000,myattempts(p))
  result2=rgeom(10000,p)
  v_mean=c(mean(result1),mean(result2))
  v_sd=c(sd(result1),sd(result2))
  v_median=c(median(result1),median(result2))
  df2=data.frame(mean=v_mean,std=v_sd,median=v_median)
  rownames(df2)<-c('myattempts','rgeom')
  df2
```

```{r Problem 1-(c)}
  library("ggplot2")
  p=0.5;
  result1=replicate(10000,myattempts(p))
  result2=rgeom(10000,p)
  df3=data.frame(myattempts=result1,rgeom=result2)
  #df3[1:6,]
  pic1=ggplot(df3)+
    geom_histogram(aes(x=df3[,1]),color="blue",binwidth=1)+
    geom_histogram(aes(x=df3[,2]),color="red",binwidth=1)+
    xlab("Distributions")+ylab("Numbers")
  pic1
  pic2=ggplot(df3)+
    geom_histogram(aes(x=df3[,2]),color="red",binwidth=1)+
    geom_histogram(aes(x=df3[,1]),color="blue",binwidth=1)+
    xlab("Distributions")+ylab("Numbers")
  pic2
```

```{r Problem 1-(d)}
  p=0.7;
  result1=replicate(10000,myattempts(p))
  result2=rgeom(10000,p)
  df4=data.frame(data=c(result1,result2),kind=c(rep('myattempts',length(result1)),rep('rgeom',length(result2))))
  pic=ggplot(df4)+
    geom_boxplot(aes(kind,data,color=kind))
  pic

```

#Problem 2
```{r Problem 2}
  generate<-function(){
    x=0
    for(i in 1:10){
      x=runif(1,0,1+x)
    }
    return(x)
  }
  m_x<-replicate(10000,generate())
  print(mean(m_x))
  df=data.frame(results=m_x)
  pic=ggplot(df)+
    geom_histogram(aes(x=results),binwidth=0.05)
  pic
```

#Problem 3
```{r Problem 3-(a)}
cat(pgamma(10,2.5,scale=5))
```

```{r Problem 3-(b)}
cat(1-pgamma(5,2.5,scale=5))
```

```{r Problem 3-(c)}
cat(pgamma(9,2.5,scale=5)-pgamma(7,2.5,scale=5))
```

```{r Problem 3-(d)}
cat(qgamma(0.95,2.5,scale=5))
```

#Problem 4
In the second case, two plots seem not to be having the same ending value.
In the third case, two plots seem not to be having the same starting value.
```{r Problem 4}
drawpic<-function(n,p){
  ave=n*p
  std=sqrt(n*p*(1-p))
  bino<-pbinom(0:n,n,p)
  normal<-pnorm(seq(0,n,n/100),ave,std)
  constant1=rep(1,n+1)
  constant2=rep(1,101)
  df1=data.frame(number=0:n,binomial=bino,constant=constant1)
  df2=data.frame(x=seq(0,n,n/100),normal=normal,constant=constant2)
  pic<-ggplot()+
    geom_col(data=df1,aes(x=number,y=binomial,width=1.0))+
    #geom_line(data=df1,aes(x=number,y=binomial,color=constant))+
    geom_line(data=df2,aes(x=x,y=normal,color=constant))+
    xlab('x')+ylab('F(x)')
  return(pic)
}

pic1<-drawpic(40,0.5)
pic1
pic2<-drawpic(40,0.9)
pic2
pic3<-drawpic(10,0.5)
pic3
```

#Problem 5
The more numbers a sample has, the more close the picture is to a straight line.
Usually bias occurs in the middle of the line, rather than the two vertexes of the line. That's because the fraction scale of the margins of the line is small and that leads to smaller bias.
```{r Problem 5}
normtest<-function(size){
  x=rnorm(size,0,1);
  pic=qqnorm(x);
  return(pic)
}
pic1<-normtest(10)
pic1
pic2<-normtest(20)
pic2
pic3<-normtest(40)
pic3
pic4<-normtest(100)
pic4
pic5<-normtest(400)
pic5
```

#Problem 6
```{r Problem 6}
num=100000
n=100

x=rexp(num,1)
Fx=pexp(x,1)
bin=(0:n)/n
bin_Fx=rep(1,n)
for(i in 1:n){
  bin_Fx[i]=mean(Fx>=bin[i]&Fx<bin[i+1])
}
df=data.frame(x=(0:(n-1))/n+1/(2*n),Fx=bin_Fx)
pic1<-ggplot(df)+
  geom_col(aes(x=x,y=Fx))+
  labs(title=bquote('Exponent'))
pic1

x=rnorm(num,0,1)
Fx=pnorm(x,0,1)
bin=(0:n)/n
bin_Fx=rep(1,n)
for(i in 1:n){
  bin_Fx[i]=mean(Fx>=bin[i]&Fx<bin[i+1])
}
df=data.frame(x=(0:(n-1))/n+1/(2*n),Fx=bin_Fx)
pic2<-ggplot(df)+
  geom_col(aes(x=x,y=Fx))+
  labs(title=bquote('Normal'))
pic2

x=rgamma(num,2.5,scale=5)
Fx=pgamma(x,2.5,scale=5)
bin=(0:n)/n
bin_Fx=rep(1,n)
for(i in 1:n){
  bin_Fx[i]=mean(Fx>=bin[i]&Fx<bin[i+1])
}
df=data.frame(x=(0:(n-1))/n+1/(2*n),Fx=bin_Fx)
pic3<-ggplot(df)+
  geom_col(aes(x=x,y=Fx))+
  labs(title=bquote('Gamma'))
pic3
```

#Bonus Problem
```{r Bonus Problem}
alpha=0.3
x1=rexp(10000,1)
x2=rexp(10000,1)
x=x1+x2
x_alpha=x^alpha
#cat(x1[1],x2[1],x[1],x_alpha[1])
qqnorm(x_alpha)
```
