```{r}
library(rstudioapi)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```

#Problem 1

###(a)
```{r}
library(ISLR)
head(Auto)
pairs(Auto)
```
###(b)
```{r}
Auto_cleaned=subset(Auto, select = -c(name))
cor(Auto_cleaned)
```

###(c)
```{r}
model1=lm(mpg~.,data=Auto_cleaned)
summary(model1)
```
Comment:
(1) Since p-value of F-statistic is low, there is a relationship between the predictors and the response.
(2) Since variables of displacement, weight, year, origin have a rather low p-value for t-statistic, they are the statistically significant predictors.
(3) When year increases or decreases by 1, the change of the response is 0.750773 or -0.750773.

###(e)
```{r}
model2=lm(mpg~.+horsepower*origin, data=Auto_cleaned)
summary(model2)
```
Comment: It seems that the interaction between horsepower and original is statistically significant.

###(f)
```{r}
model3=lm(mpg~.-horsepower+log(horsepower),data=Auto_cleaned)
summary(model3)
```
In this model, log(horsepower) seems to be statistically significant.
```{r}
model4=lm(mpg~.-horsepower+I(horsepower^2),data=Auto_cleaned)
summary(model4)
```
In this model, horsepower^2 seems to be more significant than without transformation.

```{r}
model5=lm(mpg~.-horsepower+I(horsepower^0.5),data=Auto_cleaned)
summary(model5)
```
In this model, horsepower^0.5 seems to be statistically significant.

#Problem 2

###(a)
```{r}
head(Carseats)
model6=lm(Sales~Price+Urban+US, data=Carseats)
```

###(b)
```{r}
summary(model6)
```
Comment: 
(1) When Price increases or decreases by x, the change of the response is -0.054459 x or 0.054459 x.
(2) Urban equal to yes leads to Sales -0.021916.
(3) US equal to yes leads to Sales +1.200573.

###(c)
Formula:
$$Sales=13.043469-0.054459*Price+\begin{cases}0&Urban = No\\-0.021916&Urban=Yes\end{cases}+\begin{cases}0&US=No\\1.200573&US=Yes\end{cases}$$
###(d)
Since p-values of t-statistic of Price and USYes are extremely low, we can reject the mentioned null hypothesis.

###(e)
```{r}
model7=lm(Sales~Price+US, data=Carseats)
summary(model7)
```

###(f)
According to the R-squared values, (a) and (e) fit the data not so well nor too bad.

###(g)
```{r}
confint(model7)
```