#Problem 1
```{r}
library(rstudioapi)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
bdesh<-read.csv('Bangladesh.csv')
head(bdesh)
```
#(a)
```{r}
boxplot(bdesh$Cobalt)
```
Comment: There are so many outliers if no transformation is made. I think the right transformation can explain the data better.

#(b)
```{r}
log_Cobalt=log(bdesh$Cobalt)
boxplot(log_Cobalt)
```
Comment: There are less outliers after the transformation.
#(c)
```{r}
log_Cobalt=log_Cobalt[!is.na(log_Cobalt)]
n=100
N=10000
rec_mean=numeric(N)
for (i in 1:N){
  res<-sample(log_Cobalt,n,replace=TRUE)
  rec_mean[i]<-mean(res)
}
hist(rec_mean, main='Bootstrap distribution of mean',col='blue')
abline(v=mean(rec_mean),col='red',lty=2)
```
#(d)
```{r}
bias=mean(rec_mean)-mean(log_Cobalt)
bias
```
#(e)
```{r}
sd(rec_mean)
MSE=var(rec_mean)+bias^2
MSE
```
Comment: We can make estimations for error(MSE) through the bootstrap method. In this example, the variance plays the important role in the MSE.

#(f)
```{r}
log10_Cobalt=log10(bdesh$Cobalt[!is.na(bdesh$Cobalt)])
n=100
N=10000
rec_mean=numeric(N)
for (i in 1:N){
  res<-sample(log10_Cobalt,n,replace=TRUE)
  rec_mean[i]<-mean(res)
}
bias=mean(rec_mean)-mean(log10_Cobalt)
bias
sd(rec_mean)
MSE=var(rec_mean)+bias^2
MSE
quantile(rec_mean, c(0.025,0.975))
```
Comment: The right choice of a transformation is important. It can reduce bias as well as sd efficiently.

#(g)
```{r}
actual=bdesh$Cobalt[!is.na(bdesh$Cobalt)]
rec_mean=numeric(N)
for (i in 1:N){
  res<-sample(actual,n,replace=TRUE)
  rec_mean[i]<-mean(res)
}
hist(rec_mean, main='Bootstrap distribution of mean',col='blue')
abline(v=mean(rec_mean),col='red',lty=2)
mean(rec_mean)
sd(rec_mean)
bias=mean(rec_mean)-mean(actual)
bias

```
Comment: It performs worse than the log10 transformation. So sometimes transformation for the data is necessary.

#Problem 2
```{r}
Titanic=read.csv('Titanic.csv', stringsAsFactors = FALSE)
head(Titanic)
```
#(a)
```{r}
age_sur=Titanic[Titanic$Survived==1,'Age']
age_vic=Titanic[Titanic$Survived==0,'Age']
```
#(b)
```{r}
n=100
N=100000
dif=numeric(N)
for (i in 1:N){
  sam_sur=sample(age_sur, n, replace=TRUE)
  sam_vic=sample(age_vic, n, replace=TRUE)
  dif[i]=mean(sam_sur)-mean(sam_vic)
}

```
#(c)
```{r}
quantile(dif, c(0.05,0.95))
```
Comment: The null hypothesis doesn't hold. There is difference in age between the survivors and the victims. The survivors are younger on average.
#(d)
```{r}
quantile(dif, c(0.025,0.975))
```
Comment: The null hypothesis doesn't hold. There is difference in age between the survivors and the victims. The survivors are younger on average.