#Problem 1
Only distribution in (d) is uniform. Other distributions are all not uniform.
```{r Problem 1-(a)}
a=0
b=1
X_1=runif(10000,a,b)
X_2=runif(10000,a,b)
plot.ecdf(X_1+X_2)
```

```{r Problem 1-(b)}
plot.ecdf(X_1*X_2)
```

```{r Problem 1-(c)}
X_max=rep(1,10000)
X_min=rep(1,10000)

for(i in 1:10000){
  X_max[i]=max(X_1[i],X_2[i])
  X_min[i]=min(X_1[i],X_2[i])
}
plot.ecdf(X_max)
plot.ecdf(X_min)
```

```{r Problem 1-(d)}
plot.ecdf(1-X_1)
```

#Problem 2
```{r Problem 2-(a)}
a=4
b=5
mu=2
sigma=3
library("nortest")
X=rnorm(10000,mu,sigma)
Y=a*X+b
ks.test(Y,"pnorm",a*mu+b,a*sigma)
```

```{r Problem 2-(b)}
X_1=rnorm(10000,1,2)
X_2=rnorm(10000,2,3)
X_3=rnorm(10000,3,4)
X_4=rnorm(10000,4,5)
X=X_1+X_2+X_3+X_4
ks.test(X,"pnorm",10,sqrt(54))
```

#Problem 3
AD-test don't require specific parameters and KS does require. They give the different pvalue. But if the pvalue is no minor, the distribution is just kind of normal statistically. KS-test don't like dataset containing the same values. It deal with different continuous values.
```{r Problem 3}
library(datasets)
library(dplyr)
data("iris")

head(iris)
X=iris[iris['Species']=='setosa','Sepal.Width']

ad.test(X)

m=mean(X)
std=sd(X)
ks.test(X,"pnorm",m,std)
```

#Problem 4
Proof:
(a)
P(X_min<x)=1-P(X_min>=x)=1-P(X_1>=x)*P(X_2>=x)...P(X_k>=x)
=1-e^(-k lambda x)
d(X_min<x)=k lambda e^(-k lambda x)

(b)
P(X_max<x)=P(X_1<x)*P(X_2<x)...P(X_k<x)
=(1-e^(lambda x))^k

(c)
As we know, exponential distribution with lambda is a special case of gamma distribution with parameters of (lambda,1)
And use the property of gamma distribution we have the distribution of x_sum be the gamma distribution with (lambda,k)

In fact, only X_min is again exponentially distributed.
```{r Problem 3-(a)}
k=10
X=rexp(k*10000,1)
X=matrix(X,nrow=10000,ncol=k)
X_min=apply(X,1,min)
plot.ecdf(X_min)
ks.test(X_min,k)
```

```{r Problem 3-(b)}
X_max=apply(X,1,max)
plot.ecdf(X_max)
```

```{r Problem 3-(c)}
X_sum=apply(X,1,sum)
plot.ecdf(X_sum)
ks.test(X_sum,"pgamma",k,1)
```
