#Problem 1
```{r Problem 1-(i)}
Roulette_plot<-function(p,X0,N){
  myCash = c(X0, rep(0,N)) # vector for my cash
  spins <- rbinom(N,1,p) # simulate N spins
  counter = 1 # keep track of number of games
  lastspin = 1 # initialize memory of last games
  myBet = 1
  while(myCash[counter] > 0 & counter <= N){#this goes on until I loose all my money or reaches the maximal myBet <- min(c(2*myBet,myCash[counter]))
  if(lastspin == 1){myBet <- 1}
  myCash[counter + 1] <- myCash[counter] + (2*spins[counter] - 1)*myBet
  lastspin <- spins[counter]
  counter <- counter + 1
  }
  plot(myCash, type = 'l') # plot of my cash
  abline(a = X0, b = -1/19, col = 2) # plot expected trend
}
Roulette_plot(18/38,100,500)
Roulette_plot(18/38,500,500)
Roulette_plot(18/38,1000,500)
```
If the initial amount is larger, the more likely we have larger bias from the expected line.

```{r Problem 1-(ii)}
Peter_plot<-function(p,maxBet,X0,N){
  myCash = c(X0, rep(0,N)) # vector for my cash
  spins <- rbinom(N,1,p) # simulate N spins
  counter = 1 # keep track of number of games
  lastspin = 1 # initialize memory of last games
  myBet = 1
  while(myCash[counter] > 0 & counter <= N){
  myBet <- min(c(2*myBet,myCash[counter], maxBet))
  if(lastspin == 1){myBet <- 1}
  myCash[counter + 1] <- myCash[counter] + (2*spins[counter] - 1)*myBet
  lastspin <- spins[counter]
  counter <- counter + 1
  }
  plot(myCash, type = 'l') # plot of my cash
  abline(a = X0, b = -1/19, col = 2) # plot expected trend
}
Peter_plot(18/38,20,100,1000)
Peter_plot(18/38,60,100,1000)
Peter_plot(18/38,100,100,1000)
Peter_plot(18/38,140,100,1000)

Peter_plot(18/38,20,100,600)
Peter_plot(18/38,10,100,600)
```
The larger the max number of spins we have, the more likely mycash reduces to 0(Has a more detailed picture of the whole process)
Within certain range, the larger maxbet we have, the less likely mycash reduces to 0(Longer process). But with mybet above certain value, mycash reduces to 0 rapidly.

#Problem 2
```{r Problem 2-(a)}
P <- matrix(0, ncol = 9, nrow = 9)
diag(P) <- 1/2
P[1,2] <- P[1,4] <- 1/4
P[2,1] <- P[2,3] <- P[2,5] <- 1/6
P[3,2] <- P[3,6] <- 1/4
P[4,1] <- P[4,5] <- P[4,7] <- 1/6
P[5,2] <- P[5,4] <- P[5,6] <- 1/6
P[6,3] <- P[6,5] <- 1/4
P[7,4] <- P[7,8] <- 1/4
P[8,7] <- P[8,9] <- 1/4
P[9,9] <- 1

cave_simulate<-function(steps,sample_n){
  states = rep(1,sample_n)
  for (j in 1:steps){
    for(k in 1:sample_n){
      states[k] <- sample(9,1,prob = P[states[k],])
    }
  }
  return(states)
}

results = cave_simulate(3,100000)
mean(results==3)
(P%*%P%*%P)[1,3]
```
The probability of the caveman being at position 3 at time 3 given the initial position 1.

```{r Problem 2-(b)}
step=1
P_result=P
while(1){
  step=step+1
  P_result=P_result%*%P
  max_prob=min(P_result[1:9,9])
  if(max_prob>=0.75)
    break
}
step
```