#Problem 1
```{r Problem 1-(a)}
Y = rnorm(100000,0,1)
X = floor(Y)
df=data.frame(X=X,Y=Y)
head(df)
```

```{r Problem 1-(b)}
aggdata_median <- aggregate(df,by=list(X),median)
aggdata_median
plot(aggdata_median$X,aggdata_median$Y,type='l',col='red')
```

```{r Problem 1-(c)}
aggdata_sd <- aggregate(df,by=list(X),sd)
aggdata_sd
plot(aggdata_sd$Group.1,aggdata_sd$Y,type='l',col='red')
```

#Problem 2
```{r Problem 2-(a)}
df_2=data.frame(runif(10000,0,1),runif(10000,0,1))
plot(df_2,pch=46)
plot(df_2[(df_2[1]+df_2[2])<1,],pch=46)
```

Problem 2-(b)
Points of (X,Y) lies uniformly in the triangle above. So f(x,y)=2 when x>=0 & y>=0 & x+y<1 and f(x,y)=0 otherwise. 

```{r Problem 2-(c)}
df_2_c=df_2[(df_2[1]+df_2[2])<1,]

hist(df_2_c[,1],prob=T,breaks=seq(0,1,0.025))
```

```{r Problem 2-(d)}
hist(df_2_c[,2],prob=T,breaks=seq(0,1,0.025))
```
Yes they are the same.

#Problem 3

(a)
If we compute the integral of f(x,y) on the region of {0<y<1,0<x<2}, we have the result of 4. So C equals 1/4. In fact we first compute the integral of C(x+2y) on {0<x<2}, we have C(2+4y). Then we compute the integral of C(2+4y) on {0<y<1}, we have 4C. So C=1/4.

(b)
We compute the integral of f(X,Y) on the region of {0<y<1}. Then we have f(x)=(x+1)/4 on the region of {0<x<2} and f(x)=0 otherwise.

(c)
we compute the integral of f(X,Y) on the region of {0<X<2}. Then we have f_(y)=(2y+1)/2 on the region of {0<y<1} and f_(y)=0 otherwise.

(d)
We compute that g(y)=f(x,y)/f(x)=(x+2y)/(x+1) on the region of {0<y<1} and g(y)=0 otherwise.

(e)
We compute E(Y|X) as the integral of y(x+2y)/(x+1) on the region of {0<y<1}. Then we have E(Y|X)=(3x+4)/(6x+6)