#Problem 1
Throwing Dice as Multinomial Distribution

###Rolling a die N=100 times

#####creates the function to roll a die for one time
```{r}
one.dice <- function(){
  dice <- sample(1:6, size = 1, replace = TRUE)
  return(dice)
}

one.dice()
```
#####repeat 4 times the process of rolling a die for 100 times as well as computing the frequencies of each value. Then create the frequency plot in a 2x2 form.
```{r}
par(mfrow=c(2,2))

for (i in 1:4){
sims <- replicate(100, one.dice())
table(sims)
table(sims)/length(sims)
plot(table(sims), xlab = 'Event', ylab = 'Frequency')
}
```

###Rolling a die N=10000 times
#####repeat what is done above with a much larger N=10000
```{r}
par(mfrow=c(2,2))

for (i in 1:4){
sims <- replicate(10000, one.dice())
table(sims)
table(sims)/length(sims)
plot(table(sims), xlab = 'Event', ylab = 'Frequency')
}
```

Comments:
1. When we roll a die with a bigger value of N, we have results that is closer to the distribution. That's the law of large numbers.
2. We can also use the function of rmultinomial to do the simulation directly without repeating the rolling function.

#Problem2
###(a)
```{r}
mysample=rmultinom(100000, size=3, prob=c(3/5,1/5,1/5))
mean(mysample[1,]==1&mysample[2,]==2)
dmultinom(c(1,2,0),prob=c(3/5,1/5,1/5))
```
###(b)
```{r}
x1_dist=table(mysample[1,])/length(mysample[1,])
plot(x1_dist,xlab='count',ylab='Probability')
```

#Problem3
```{r}
library(tidyverse)
library(mvtnorm)
library(plotly)
library(MASS)
library(ggplot2)
```

#Simulate multivariate normal data

#####creates the covariance matrix
```{r}
sigma <- matrix(c(4,2,2,3), ncol = 2)
sigma
```
#####generates the samples
```{r}
means <- c(0, 0)
n <- 1000

set.seed(42)
x <- rmvnorm(n = n, mean = means, sigma = sigma)
str(x)
```

```{r}
d <- data.frame(x)
names(d)
```

#Plotting

###Plotting univariate (sampled) normal data
```{r}
d %>% 
  ggplot(aes(x = X1)) +
  geom_density()
```
Observation: The distribution of data seems to be kind of close to a normal distribution.

###Plot theoretic normal curve
```{r}
p1 <- data_frame(x = -3:3) %>% 
  ggplot(aes(x = x)) +
  stat_function(fun = dnorm, n = n)
p1
```
Observation: The normal distribution plot has a standard symmetric and smooth curve.

###Plotting multivariate data

#####2D density
```{r}
p2 <- ggplot(d, aes(x = X1, y = X2)) +
  geom_point(alpha = .5) +
  geom_density_2d()
p2
```
Observation: We can kind of get brief information about which part is dense and which part is sparse from the contour curve in 2D-density plot.

#####Geom binhex

```{r}
p3 <- ggplot(d, aes(x = X1, y = X2)) +
  geom_point(alpha = .5) +
  geom_bin2d() +
  scale_fill_viridis_c()

p3
```
Observation: The 2d-bin plot uses the color to describe the density of the points.
 
#####2D histogram (heatmap) with plotly
```{r}
(p <- plot_ly(d, x = ~X1, y = ~X2))
```
Observation: That's a basic 2D scatter plot.

```{r}
add_histogram2d(p)
```
Observation: The 2d-histogram plot is kind of like the 2d-bin plot, but with a full domain.

#####2D contour with plotly
```{r}
add_histogram2dcontour(p)
```
Observation: The contour plot uses different colors to describe the density of the points.

###3D plot

#####Surface

```{r}
dens <- kde2d(d$X1, d$X2)

plot_ly(x = dens$x,
        y = dens$y,
        z = dens$z) %>% add_surface()
```
Observation: We first generate values of density on a meshgrid and simply add a smooth surface to it.

#####3D Scatter
```{r}
d$dens <- dmvnorm(x = d)
```

```{r}
p4 <- plot_ly(d, x = ~ X1, y = ~ X2, z = ~ dens,
              marker = list(color = ~ dens,
                            showscale = TRUE)) %>% 
  add_markers()

p4
```
Observation: 3D-scatter plot has the density value being the z-axis value of original x,y-axis. 


Comments:(Observations for each plot is just attached under that plot)
1. When we use plot_ly to create 3D plots, we need to first convert the original data into density values on a 2D-meshgrid.
2. We can briefly get information about the density distribution from the contour curves in the 2D-density plot.